Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-06-15 doc/ms.tex

\correspondingauthor{Yi Cao}
\email{ycao16@uw.edu}

@@

Early observations of type Ia supernovae (SNe) provide a unique probe of their progenitor systems and explosion physics. Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young Type Ia supernova, \abc. The initial detection of the SN was made only $0.18$~d after the time of first light. In the $\sim$24 hr after discovery \abc\ rose by $\sim$2 mag in the $g_\mathrm{PTF}$ band, which is very rare for young type Ia SNe. Furthermore, by measuring the evolution of the photospheric velocity we determine that the time of explosion for \abc\ is approximately equal to the time of first light. Spectra obtained in the week after explosion reveal the presence of strong \ion{C}{2} absorption, which steadily fades over that time period. We show that the unusually fast, near-linear rise in flux for \abc\ cannot be explained by either SN shock breakout and the assciated subsequent cooling or the collision of the SN ejecta with a stellar companion. Instead, we show that each of the unusual characteristics of \abc: (i) the rapid, near-linear rise, (ii) the lack of a dark period between explosion and first light, and (iii) the strong lines from ionized carbon in the earliest spectra, can all be explained if radioactive $^{56}$Ni is strongly mixed throughout the SN ejecta. In the next few years, dozens of very young \textit{normal} SNe Ia will be discovered, and observations similar to those presented here will constrain the white dwarf explosion mechanism.

@@

Early phase observations of SNe Ia from a white dwarf (WD)$+$non-degenarate binary
may detect excess emission, relative to most type Ia SNe, due to the 
collision of the SN ejecta with the non-degenerate companion 
\citep{1973ApJ...186.1007W,2010ApJ...708.1025K}. This excess 
emission was first detected in iPTF\,14atg  \citep{2015Natur.521..328C}, a low-velocity SN Ia with a significant and declining ultraviolet (UV) pulse detected within a
few days of the SN explosion. This UV pulse is best interpreted as a
SN ejecta-companion collision. While such emission requires a 
favorable geometric alignment and is only expected in $\lesssim$ 
10\% of SNe Ia \citep{2010ApJ...708.1025K}, many studies have 
searched for signatures of an ejecta-companion interaction, 
typically resulting in non-detections 
(e.g., \citealt{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
  2012ApJ...744L..17B,2015Natur.521..332O,
  2013ApJ...778L..15Z,2015ApJ...799..106G,2016ApJ...826..144S,
  2015ApJS..221...22I}). A possible exception is SN\,2012cg, 
which exhibited excess blue emission in its early-phase light curve 
\citet{2016ApJ...820...92M} (though see 
\citealt{2016arXiv161007601S} for an interpretation that does not 
invoke ejecta-companion interaction). 
% With only $\sim 10\%$ of single-degenerate progenitors occupying the preferred binary geometry for us to see the collision
% signatures, it is not surprising that there are few confirmed detections in the literature \ycao{ref?}.

@@

In this paper, we report observations of an extraordinarily young SN
Ia, \abc, which was discovered by the intermediate Palomar
Transient Factory (iPTF) on 2016 April $3.36$\footnote{All times in this
  paper are in UTC.} at $\textrm{R.A.}=13^h34^m45.49^s$,
$\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of
$21.31\pm0.27$ \citep{2016ATel.8907....1M}. The
transient is spatially coincident with a tidal tail of the galaxy
NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1 d prior to discovery, and rose by $\sim$2 mag in the 24 hr following its initial detection. Our spectroscopic follow-up
compaign classified \abc\ as a normal SN Ia
\citep{2016ATel.8909....1C}. Our observations and analysis provide multiple lines of evidence that the $^{56}$Ni produced by \abc\ was strongly mixed throughout the ejecta.

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{logLC_with_colors.pdf}
  \caption{Photometric evolution of \abc. \textit{Top}: The $g$-band
  light curve of \abc. Observations from different 
  telescopes are shown with different symbols. Time is measured in 
  rest-frame d relative to the time of first light, $t_0$ (see 
  \S\ref{sec:lc_fit}). Note that the horizonal axis is shown with a linear scale 
  for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$ and a 
  $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. The solid curve 
  represents the best-fit model from SALT2 
  (\S\ref{sec:classification}). The black ticks near the
  bottom of the panel show epochs of spectroscopic observations.
  \textit{Bottom}: Color curves of \abc. Each color curve is 
  represented with a different color, with each symbol corresponding 
  to a different instrument, as detailed in the legend. Magnitude 
  offsets applied to each color curve are also shown.
  }
  \label{fig:lightcurve}
\end{figure*}

@@

After discovery, photometric observations in the $g'$, $r'$ and $i'$
filters were obtained with the SED Machine 
(SEDm; Blagorodnova et al.\ 2017, in prep.) mounted on the Palomar Observatory 
60-inch telescope (P60). We utilized the Fremling Automated Pipeline \citep{2016A&A...593A..68F} to subtract galaxy light from the SEDm images using achival Sloan Digital Sky Survey (SDSS) images as a reference. This pipeline then performed forced-PSF photometry at the location of \abc, which is calibrated to the SDSS catalog \citep{2014ApJS..211...17A}.

@@

\begin{deluxetable*}{cccccc}
  \tablecaption{Spectroscopic observations of \abc\ \label{tab:spec_obs_log}}
  \tablehead{
    \colhead{Observation MJD} & \colhead{SN phase} & \colhead{Telescope} &
    \colhead{Instrument} & \colhead{Wavelength Coverage (\AA)}
  }
  \startdata
  $57483.26$ & $-16.4$ & DCT & DeVeny\tablenotemark{1} & $3301$--$7499$ \\
  $57483.88$ & $-15.8$ & Gemini-North & GMOS\tablenotemark{2} & $3800$--$9200$ \\
  $57484.51$ & $-15.1$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
  $57486.51$ & $-13.1$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
  $57488.38$ & $-11.3$ & Keck-I & LRIS\tablenotemark{4} & $3055$--$10411$ \\
  $57489.51$ & $-10.1$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
  $57490.40$ & $ -9.3$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
  $57491.55$ & $ -8.1$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
  $57492.20$ & $ -7.5$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24550$ \\
  $57494.00$ & $ -5.7$ & VLT & UVES\tablenotemark{7} & \\
  $57503.32$ & $ +3.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9999$ \\
  $57506.00$ & $ +6.3$ & NOT & ALFOSC\tablenotemark{8} & $3602$--$8098$ \\
  $57508.27$ & $ +8.6$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
  $57518.42$ & $+18.8$ & Keck-I & LRIS\tablenotemark{4} & $3071$--$10208$ \\
  $57520.03$ & $+20.4$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24789$ \\
  $57529.40$ & $+29.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
  $57542.41$ & $+42.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
  $57550.40$ & $+50.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
  $57562.38$ & $+62.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
  \enddata
  \tablenotetext{1}{The Deveny Spectrograph \citep{2014SPIE.9147E..2NB}}
  \tablenotetext{2}{The Gemini Multi-Object Sectrograph \citep{2004PASP..116..425H}}
  \tablenotetext{3}{DEep Imaging Multi-Object Spectrograph \citep{2003SPIE.4841.1657F}}
  \tablenotetext{4}{Low-Resolution Imaging Spectrometer \citep{1995PASP..107..375O}}
  \tablenotetext{5}{FLOYDS \url{https://lco.global/observatory/instruments/floyds}}
  \tablenotetext{6}{X-shooter \citep{XShooter}}
  \tablenotetext{7}{Ultraviolet and Visual Echelle Spectrograph \citep{2000SPIE.4008..534D}}
  \tablenotetext{8}{The Andalucia Faint Object Spectrograph and Camera \url{http://www.not.iac.es/instruments/alfosc}}
\end{deluxetable*}

@@

A detailed study of the reddening towards \abc\ is presented in a 
companion paper (Ferretti et al.\ 2017, submitted). Briefly, the 
foreground Galactic extinction toward \abc\
is $E(B-V) = 0.0279 \, \mathrm{mag}$ \citep{2011ApJ...737..103S}. The high-resolution spectra presented in Ferretti et al.\ (2017) show multiple absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets. While the equivalent width (EW) of these lines is quite large, implying a large amount of extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal type Ia SN\,2011fe and find evidence for only a small amount of extinction. The empircal relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017). For the remainder of our analysis we therefore adopt a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.0779 \, \mathrm{mag}$.

\subsection{Classfication}
\label{sec:classification}

@@

The time of first light for SNe is usually estimated by 
extrapolating early-phase light curves to determine when the 
SN is equal to 0. Assuming an ideal exapnding fireball with 
constant temperature, \citet{1982ApJ...253..785A} derives that $f 
\propto t^2$, where $f$ is the SN flux and $t$ is the time since 
explosion. Despite the basic assumption of a constant temperature at 
early times, multiple studies have found that the early emission 
from type Ia SNe can be described as a power law in time, with 
power-law index consistent with 2, i.e. $f \propto t^2$ (e.g., \citep{2006AJ....132.1707C, 2010ApJ...712..350H, 2011MNRAS.416.2607G}).

@@

As previously noted, $t_0$ does not correspond to the time of 
explosion, $t_\mathrm{exp}$, for type Ia SNe as the SN may 
experience a dark phase following shock breakout before radioactive 
energy can difuse to the photosphere. \citet{2014ApJ...784...85P} 
instead suggest that measurements of the photospheric velocity be 
used to determine $t_\mathrm{exp}$ given that the ejecta begin 
expanding from the moment of explosion.  Assuming a
constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P} 
find that the photospheric velocity evolves as
$v_{ph}\propto(t-t_{exp})^{-0.22}$. While the photospheric velocity
is not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
can be used as a proxy
\citep{2014ApJ...784...85P,2016ApJ...826..144S}.

@@

The detection of \ion{C}{2} in SNe Ia spectra is relatively rare
as it requires both unburned carbon, which is likely only present in the outermost layers of the ejecta, and non-local thermal equilibrium effects in order to excite the ionized carbon (e.g., \citealt{2007ApJ...654L..53T}). Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receeded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak. While we caution that the sample of normal SNe Ia with spectra taken within a few days of explosion is small, SN\,2013dy is the only other object known to have strong \ion{C}{2} features like \abc\ \citet{2013ApJ...778L..15Z}. As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the anomously strong \ion{C}{2} absorption observed shortly after explosion.

@@

While examining observations of SN\,2011fe in the context of DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24-48 hr after explosion. These discrepancies can be somewhat improved if the newly synthesized $^{56}$Ni is artificailly mixed throughout the SN ejecta (see \S\ref{sec:Ni_mixing} for further details on the importance of mixing). Instead, \citet{2014MNRAS.441..532D} find that PDD models provide a better match to observations. Briefly, the diffuse material surrounding the WD heats the outer layers of the SN ejecta leading to a steeper more luminous rise, with bluer colors in the few days after explosion. Importantly, the PDD models are nearly indistinguishable from DD models around and post peak.

@@

\item The strong and short-lived carbon features seen in the 
earliest spectra of \abc\ can only be explained if there is incomplete burning during the explosion and there is a non-thermal 
radiation source in the outermost layers of the ejecta to excite the ionized carbon. $^{56}$Ni decay is the likely source of the nonthermal emission, providing another piece of evidence for strong mixing in the ejecta of \abc.

>>>>

\correspondingauthor{A.~A.~Miller}
\email{amiller@northestern.edu}

@@

Early observations of type Ia supernovae (SNe) provide a unique probe of their progenitor systems and explosion physics. Here, we report the intermediate Palomar Transient Factory (iPTF) discovery of an extraordinarily young Type Ia supernova, \abc. The initial detection of the SN was made only $0.18$~d after the time of first light. In the $\sim$24 hr after discovery, \abc\ rose by $\sim$2 mag in the $g_\mathrm{PTF}$ band, which is very rare for young type Ia SNe. Furthermore, by measuring the evolution of the photospheric velocity we determine that the time of explosion for \abc\ is approximately equal to the time of first light. Spectra obtained in the week after explosion reveal the presence of strong \ion{C}{2} absorption, which steadily fades over that time period. We show that the unusually fast, near-linear rise in flux for \abc\ cannot be explained by either SN shock breakout and the associated subsequent cooling or the collision of the SN ejecta with a stellar companion. Instead, we show each of the unusual characteristics of \abc: (i) the rapid, near-linear rise, (ii) the lack of a dark period between explosion and first light, and (iii) the strong lines from ionized carbon in the earliest spectra, can all be explained if radioactive $^{56}$Ni is strongly mixed throughout the SN ejecta. In the next few years, dozens of very young \textit{normal} SNe Ia will be discovered, and observations similar to those presented here will constrain the white dwarf explosion mechanism.

@@

Early phase observations of SNe Ia from a white dwarf (WD)$+$non-degenerate binary
may detect excess emission, relative to most type Ia SNe, due to the 
collision of the SN ejecta with the non-degenerate companion 
\citep{1973ApJ...186.1007W,2010ApJ...708.1025K}. This excess 
emission was first detected in iPTF\,14atg  \citep{2015Natur.521..328C}, a low-velocity SN Ia with a significant and declining ultraviolet (UV) pulse detected within a
few days of the SN explosion. This UV pulse is best interpreted as a
SN ejecta-companion collision. While such emission requires a 
favorable geometric alignment and is only expected in $\lesssim$ 
10\% of SNe Ia \citep{2010ApJ...708.1025K}, many studies have 
searched for signatures of an ejecta-companion interaction, 
typically resulting in non-detections 
(e.g., \citealt{2010ApJ...722.1691H,2011ApJ...741...20B,2012ApJ...744...38F,
  2012ApJ...744L..17B,2015Natur.521..332O,
  2013ApJ...778L..15Z,2015ApJ...799..106G,2016ApJ...826..144S,
  2015ApJS..221...22I}). A possible exception is SN\,2012cg, 
which exhibited excess blue emission in its early-phase light curve 
\citet{2016ApJ...820...92M} (though see 
\citealt{2016arXiv161007601S} for an interpretation that does not 
invoke ejecta-companion interaction). 
% With only $\sim 10\%$ of single-degenerate progenitors occupying the preferred binary geometry for us to see the collision
% signatures, it is not surprising that there are few confirmed detections in the literature \ycao{ref?}.

@@

In this paper, we report observations of an extraordinarily young SN
Ia, \abc, which was discovered by the intermediate Palomar
Transient Factory (iPTF) on 2016 April $3.36$\footnote{All times in this
  paper are in UTC.} at $\textrm{R.A.}=13^h34^m45.49^s$,
$\textrm{Dec.}=+13^d51^m14.3^s$ (J2000) with a $g_\mathrm{PTF}$-band magnitude of
$21.31\pm0.27$ \citep{2016ATel.8907....1M}. The
transient is spatially coincident with a tidal tail of the galaxy
NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected to a limit of $g=22.1$\,mag on April $2.42$, less than 1 d prior to discovery, and rose by $\sim$2 mag in the 24 hr following its initial detection. Our spectroscopic follow-up
campaign classified \abc\ as a normal SN Ia
\citep{2016ATel.8909....1C}. Our observations and analysis provide multiple lines of evidence that the $^{56}$Ni produced by \abc\ was strongly mixed throughout the ejecta.

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{logLC_with_colors.pdf}
  \caption{Photometric evolution of \abc. \textit{Top}: The $g$-band
  light curve of \abc. Observations from different 
  telescopes are shown with different symbols. Time is measured in 
  rest-frame d relative to the time of first light, $t_0$ (see 
  \S\ref{sec:lc_fit}). Note that the horizontal axis is shown with a linear scale 
  for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$ and a 
  $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. The solid curve 
  represents the best-fit model from SALT2 
  (\S\ref{sec:classification}). The black ticks near the
  bottom of the panel show epochs of spectroscopic observations.
  \textit{Bottom}: Color curves of \abc. Each color curve is 
  represented with a different color, with each symbol corresponding 
  to a different instrument, as detailed in the legend. Magnitude 
  offsets applied to each color curve are also shown.
  }
  \label{fig:lightcurve}
\end{figure*}

@@

After discovery, photometric observations in the $g'$, $r'$ and $i'$
filters were obtained with the SED Machine 
(SEDm; Blagorodnova et al.\ 2017, in prep.) mounted on the Palomar Observatory 
60-inch telescope (P60). We utilized the Fremling Automated Pipeline \citep{2016A&A...593A..68F} to subtract galaxy light from the SEDm images using archival Sloan Digital Sky Survey (SDSS) images as a reference. This pipeline then performed forced-PSF photometry at the location of \abc, which is calibrated to the SDSS catalog \citep{2014ApJS..211...17A}.

@@

\begin{deluxetable*}{cccccc}
  \tablecaption{Spectroscopic observations of \abc\ \label{tab:spec_obs_log}}
  \tablehead{
    \colhead{Observation MJD} & \colhead{SN phase} & \colhead{Telescope} &
    \colhead{Instrument} & \colhead{Wavelength Coverage (\AA)}
  }
  \startdata
  $57483.26$ & $-16.4$ & DCT & DeVeny\tablenotemark{1} & $3301$--$7499$ \\
  $57483.88$ & $-15.8$ & Gemini-North & GMOS\tablenotemark{2} & $3800$--$9200$ \\
  $57484.51$ & $-15.1$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
  $57486.51$ & $-13.1$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
  $57488.38$ & $-11.3$ & Keck-I & LRIS\tablenotemark{4} & $3055$--$10411$ \\
  $57489.51$ & $-10.1$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
  $57490.40$ & $ -9.3$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
  $57491.55$ & $ -8.1$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
  $57492.20$ & $ -7.5$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24550$ \\
  $57494.00$ & $ -5.7$ & VLT & UVES\tablenotemark{7} & \\
  $57503.32$ & $ +3.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3300$--$9999$ \\
  $57506.00$ & $ +6.3$ & NOT & ALFOSC\tablenotemark{8} & $3602$--$8098$ \\
  $57508.27$ & $ +8.6$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
  $57518.42$ & $+18.8$ & Keck-I & LRIS\tablenotemark{4} & $3071$--$10208$ \\
  $57520.03$ & $+20.4$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24789$ \\
  $57529.40$ & $+29.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
  $57542.41$ & $+42.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
  $57550.40$ & $+50.8$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
  $57562.38$ & $+62.7$ & LCOGT-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
  \enddata
  \tablenotetext{1}{The Deveny Spectrograph \citep{2014SPIE.9147E..2NB}}
  \tablenotetext{2}{The Gemini Multi-Object Spectrograph \citep{2004PASP..116..425H}}
  \tablenotetext{3}{DEep Imaging Multi-Object Spectrograph \citep{2003SPIE.4841.1657F}}
  \tablenotetext{4}{Low-Resolution Imaging Spectrometer \citep{1995PASP..107..375O}}
  \tablenotetext{5}{FLOYDS \url{https://lco.global/observatory/instruments/floyds}}
  \tablenotetext{6}{X-shooter \citep{XShooter}}
  \tablenotetext{7}{Ultraviolet and Visual Echelle Spectrograph \citep{2000SPIE.4008..534D}}
  \tablenotetext{8}{The Andalucia Faint Object Spectrograph and Camera \url{http://www.not.iac.es/instruments/alfosc}}
\end{deluxetable*}

@@

A detailed study of the reddening towards \abc\ is presented in a 
companion paper (Ferretti et al.\ 2017, submitted). Briefly, the 
foreground Galactic extinction toward \abc\
is $E(B-V) = 0.0279 \, \mathrm{mag}$ \citep{2011ApJ...737..103S}. The high-resolution spectra presented in Ferretti et al.\ (2017) show multiple absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets. While the equivalent width (EW) of these lines is quite large, implying a large amount of extinction (e.g., \citealt{2012MNRAS.426.1465P}), Ferretti et al.\ compare the evolution of \abc\ to the well-observed normal type Ia SN\,2011fe and find evidence for only a small amount of extinction. The empirical relation between the EW of \ion{Na}{1}\,D and extinction is known to have a large scatter, and thus, we instead adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for \abc\ (Ferretti et al.\ 2017). For the remainder of our analysis we therefore adopt a total, Galactic $+$ host galaxy, line-of-sight extinction of $E(B-V) = 0.0779 \, \mathrm{mag}$.

\subsection{Classification}
\label{sec:classification}

@@

The time of first light for SNe is usually estimated by 
extrapolating early-phase light curves to determine when the 
SN is equal to 0. Assuming an ideal expanding fireball with 
constant temperature, \citet{1982ApJ...253..785A} derives that $f 
\propto t^2$, where $f$ is the SN flux and $t$ is the time since 
explosion. Despite the basic assumption of a constant temperature at 
early times, multiple studies have found that the early emission 
from type Ia SNe can be described as a power law in time, with 
power-law index consistent with 2, i.e. $f \propto t^2$ (e.g., \citep{2006AJ....132.1707C, 2010ApJ...712..350H, 2011MNRAS.416.2607G}).

@@

As previously noted, $t_0$ does not correspond to the time of 
explosion, $t_\mathrm{exp}$, for type Ia SNe as the SN may 
experience a dark phase following shock breakout before radioactive 
energy can diffuse to the photosphere. \citet{2014ApJ...784...85P} 
instead suggest that measurements of the photospheric velocity be 
used to determine $t_\mathrm{exp}$ given that the ejecta begin 
expanding from the moment of explosion.  Assuming a
constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P} 
find that the photospheric velocity evolves as
$v_{ph}\propto(t-t_{exp})^{-0.22}$. While the photospheric velocity
is not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
can be used as a proxy
\citep{2014ApJ...784...85P,2016ApJ...826..144S}.

@@

The detection of \ion{C}{2} in SNe Ia spectra is relatively rare
as it requires both unburned carbon, which is likely only present in the outermost layers of the ejecta, and non-local thermal equilibrium effects in order to excite the ionized carbon (e.g., \citealt{2007ApJ...654L..53T}). Spectra obtained around or after $T_{B_\mathrm{max}}$ rarely show \ion{C}{2} as the photosphere has receded from the outermost ejecta, while pre-max spectra show evidence for \ion{C}{2} in $\sim$1/4 of all normal SNe Ia (e.g., \citealt{2011ApJ...732...30P,2012MNRAS.425.1917S,2011ApJ...743...27T}), but the signatures are typically weak. While we caution that the sample of normal SNe Ia with spectra taken within a few days of explosion is small, SN\,2013dy is the only other object known to have strong \ion{C}{2} features like \abc\ \citet{2013ApJ...778L..15Z}. As a counterexample, SN\,2011fe only exhibited weak \ion{C}{2} features in its first spectra
\citep{2012ApJ...752L..26P}. Thus, models of \abc\ must explain the anomalously strong \ion{C}{2} absorption observed shortly after explosion.

@@

While examining observations of SN\,2011fe in the context of DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24-48 hr after explosion. These discrepancies can be somewhat improved if the newly synthesized $^{56}$Ni is artificially mixed throughout the SN ejecta (see \S\ref{sec:Ni_mixing} for further details on the importance of mixing). Instead, \citet{2014MNRAS.441..532D} find that PDD models provide a better match to observations. Briefly, the diffuse material surrounding the WD heats the outer layers of the SN ejecta leading to a steeper more luminous rise, with bluer colors in the few days after explosion. Importantly, the PDD models are nearly indistinguishable from DD models around and post peak.

@@

\item The strong and short-lived carbon features seen in the 
earliest spectra of \abc\ can only be explained if there is incomplete burning during the explosion and there is a non-thermal 
radiation source in the outermost layers of the ejecta to excite the ionized carbon. $^{56}$Ni decay is the likely source of the non-thermal emission, providing another piece of evidence for strong mixing in the ejecta of \abc.
